### 2016-02-02 mcmc.tex
abstract tweaks

\begin{abstract}
Markov Chain Monte Carlo (MCMC) methods for sampling probability
distribution functions (combined with abundant computational resources)
have transformed the sciences.
Here we give a brief overview of basic MCMC methods and then turn to
practical advice for their use in real inference problems.
We give advice on method choice, tuning for performance,
methods for initialization, tests of convergence, and use of the chain
output to produce parameter estimates with associated uncertainties.
\end{abstract}

>>>>

\begin{abstract}
Markov Chain Monte Carlo (MCMC) methods for sampling probability
distribution functions (combined with abundant computational resources)
have transformed the sciences.
Here we give a brief overview of the most basic MCMC method and then turn to
practical advice for the use of MCMC in real inference problems.
We give advice on method choice, tuning for performance,
methods for initialization, tests of convergence, troubleshooting, and use of the chain
output to produce or report parameter estimates with associated uncertainties.
\end{abstract}
